---
title: "homework3"
author: "Hyeonho Lee"
date: "2018년 8월 23일"
output: 
  pdf_document: 
    latex_engine: xelatex
  html_document: default
  word_document:
    highlight: tango
mainfont: NanumGothic
header-includes :
  - \usepackage{kotex}
---


```{r message=FALSE, warning=FALSE, include=FALSE}
library(tidyr)
library(dplyr)
library(OpenMx)
library(broom)
library(ggplot2)
data(twinData)
twinData <- as_tibble(twinData)
```

#  &nbsp;


Exercises 8  
Repeat exercise #3. This time, use the variables cohort, zygosity to facet, and use different colors to indicate the subgroups for which the heights are significantly similar. Comment on your finding.

&nbsp;
```{r warning=FALSE}
condition = twinData %>% group_by(cohort,zygosity) %>% 
  do(tidy( cor.test(~ ht1 + ht2, alternative = "greater" , data = . ))) %>% 
  select(cohort,zygosity,estimate)

twinData = merge(twinData, condition, by = c('cohort', 'zygosity'))

twinData %>% ggplot(mapping = aes(ht1,ht2,color=estimate)) + 
  geom_point() + facet_grid(rows = vars(cohort), cols = vars(zygosity))
```
상관계수가 0.5이상은 그룹은 MZFF, MZMM, older, younger, DZMM의 older 5개의 그룹이 있다. 
나머지 그룹은 0.5미만임을 알 수 있다.

#  


Exercises 9  
Repeat exercise #8, but compare weight this time. You should be able to recycle almost all code chunks.

&nbsp;
```{r warning=FALSE}
condition2 = twinData %>% group_by(cohort,zygosity) %>%  
  do(tidy( cor.test(~ wt1 + wt2, alternative = "greater" , data = . ))) %>% 
  select(cohort,zygosity,estimate)

twinData = twinData %>% select(-estimate) %>% merge(condition2, by = c('cohort', 'zygosity'))

twinData %>% ggplot(mapping = aes(wt1,wt2,color=estimate)) + 
  geom_point() + facet_grid(rows = vars(cohort), cols = vars(zygosity))
```
4개의 그룹만이(MZFF, MZMM) 0.5이상의 상관관계가 있다.
#  &nbsp;  


#  &nbsp;  


## &nbsp;  

  
&nbsp;

  
&nbsp;


Exercises 10  
Recreate the following graphic. This involves transforming twinData into a narrow form using gather(). You might want to take a look at Lecture 7 note for boxplots.


&nbsp;


```{r}
twinData_1 = twinData %>% select(ht1, ht2) %>% gather(key = "order", value = "heigth") %>% 
  cbind(twinData$cohort, twinData$zygosity)
colnames(twinData_1)[3:4] = c('cohort', 'zygosity')

twinData_1 %>% na.omit() %>% ggplot(mapping = aes(order, heigth)) +
  geom_boxplot() + facet_grid(rows = vars(cohort), cols = vars(zygosity))
```


#  &nbsp;




Exercises 11  
Inspect the data graphic. Is there any need to adjust the hypothesis (posed in Question #2)?  
Are the first-born taller than the second-born?

전체 데이터를 보았을 때 상관성이 있어 보였으나, 각 범주로 나누어 비교해 본 결과, DZOS 경우에만 키의 차이를 
보이는 것을 볼 수 있다.


&nbsp;


&nbsp;


&nbsp;


&nbsp;


Exercises 12

Use the paired t-test to test whether the first-born’s height is significantly different from the second-born for each subgroup.



Why do we use the paired t-test, as opposed to using the two-sample t-test?
```{r}
twinData_t.test = twinData %>% group_by(cohort, zygosity) %>% 
  do(tidy(t.test(.$ht1, .$ht2, data=., paired = TRUE)))

knitr::kable(twinData_t.test[,c(1:5,9,10)], caption = 't-test')
```


쌍둥이 이기 때문에 한 집단에 대한 비교로 생각 할 수 있고, 그러므로 paired 비교가 적합하다.


&nbsp;


&nbsp;


Test whether there is a difference with significance level 5%, for each subgroup.
```{r}
twinData_t.test = twinData %>% group_by(cohort, zygosity) %>% 
  do(tidy(t.test(.$ht1, .$ht2, data=., paired = TRUE, conf.level = 0.95)))

knitr::kable(twinData_t.test[,c(1,2,3,7,8)], caption = 'significance level 5%')
```




Finally, recreate the above graphic with different colors indicating the results of t-tests.
```{r warning=FALSE}
twinData_1 = merge(twinData_1, twinData_t.test, by = c('cohort', 'zygosity'))

twinData_1 %>% ggplot(mapping = aes(order, heigth, fill = p.value)) +
  geom_boxplot() + facet_grid(rows = vars(cohort), cols = vars(zygosity))
```