---
title: "crm_report"
author: "Hyeonho Lee"
date: "2018년 8월 23일"
output: 
  pdf_document: 
    latex_engine: xelatex
  html_document: default
  word_document:
    highlight: tango
mainfont: NanumGothic
---

data load
```{r}
library(dplyr)
mailorder = read.csv('D:/second semester/crm/mailorder.csv')
```


1. Randomly select 500 customers in the validation sample. Calculate the number of customers who actually made purchases. 
(This is the baseline case. That is, it represents the hit rate without employing models.)
```{r}
set.seed(1234)
mailorder1 = head(mailorder, 2000)
mailorder2 = tail(mailorder, 2000)

ind = sample(1:nrow(mailorder2), nrow(mailorder2), replace = FALSE)
mailorder2_1 = mailorder2[ind <= 500,]

mean(mailorder2$purchase)
```


2. Create 222 RFM codes for estimation and validation sample. Note that the median of recency, 0.5(recency) is 12, 0.5(frequency) is 2, and 0.5(monetary) = $209. Hence,
       
Based on the RFM analysis of the estimation sample, select 500 customers (in the validation sample) with the highest purchase potentials. Calculate the number of customers who actually made purchases. 

```{r}
mailorder1$R = cut(mailorder1$recency, breaks = c(min(mailorder1$recency), 12, 
                                                  max(mailorder1$recency)),include.lowest = T, labels = c(2,1))
mailorder1$F = cut(mailorder1$frequency, breaks = c(min(mailorder1$frequency)-1, 2, 
                                                    max(mailorder1$frequency)),rigth = T, labels = c(1, 2))
mailorder1$M = cut(mailorder1$monetary, breaks = c(min(mailorder1$monetary)-1, 208, 
                                                   max(mailorder1$monetary)),rigth = T, labels = c(1, 2))
mailorder2$R = cut(mailorder2$recency, breaks = c(min(mailorder2$recency), 12, 
                                                  max(mailorder2$recency)),include.lowest = T, labels = c(2,1))
mailorder2$F = cut(mailorder2$frequency, breaks = c(min(mailorder2$frequency)-1, 2, 
                                                    max(mailorder2$frequency)),rigth = T, labels = c(1, 2))
mailorder2$M = cut(mailorder2$monetary, breaks = c(min(mailorder2$monetary)-1, 208, 
                                                   max(mailorder2$monetary)),rigth = T, labels = c(1, 2))
mailorder1$R = varhandle::unfactor(mailorder1$R)
mailorder1$F = varhandle::unfactor(mailorder1$F)
mailorder1$M = varhandle::unfactor(mailorder1$M)
mailorder2$R = varhandle::unfactor(mailorder2$R)
mailorder2$F = varhandle::unfactor(mailorder2$F)
mailorder2$M = varhandle::unfactor(mailorder2$M)


mean_pur = mailorder1 %>% select(R, F, M, purchase) %>% group_by(R, F, M) %>% 
  summarise(mean_purchase = mean(purchase))%>% arrange(desc(mean_purchase))

for( i in 1:nrow(mailorder2))
{
  for( j in 1:nrow(mean_pur))
  {
    if(mean_pur$R[j] == mailorder2$R[i] &
       mean_pur$F[j] == mailorder2$F[i] &
       mean_pur$M[j] == mailorder2$M[i])
    {
      mailorder2$mean_purchase[i] = mean_pur$mean_purchase[j]
    }
  }  
}


mailorder2 %>% select(purchase, mean_purchase) %>% arrange(desc(mean_purchase)) %>% 
  head(500) %>% summarise(mean = mean(purchase))


```

3. Create 555 RFM codes for estimation and validation sample. Use the following rules that divide the sample into five (approximately) equal segments. 
Hence, Based on the RFM analysis of the estimation sample, select 500 customers (in the validation sample) with the highest purchase potentials. 
Calculate the number of customers who actually made purchases.

```{r}
mailorder1$R = cut(mailorder1$recency, breaks = c(min(mailorder1$recency), 4, 8, 12, 16, 
                                                  max(mailorder1$recency)),include.lowest = T, labels = c(5,4,3,2,1))
mailorder1$F = cut(mailorder1$frequency, breaks = c(min(mailorder1$frequency)-1, 1, 2, 5, 9, 
                                                    max(mailorder1$frequency)),rigth = T, labels = c(1,2,3,4,5))
mailorder1$M = cut(mailorder1$monetary, breaks = c(min(mailorder1$monetary)-1, 113, 181, 242, 299, 
                                                   max(mailorder1$monetary)),rigth = T, labels = c(1,2,3,4,5))
mailorder2$R = cut(mailorder2$recency, breaks = c(min(mailorder2$recency), 4, 8, 12, 16, 
                                                  max(mailorder2$recency)),include.lowest = T, labels = c(5,4,3,2,1))
mailorder2$F = cut(mailorder2$frequency, breaks = c(min(mailorder2$frequency)-1, 1, 2, 5, 9, 
                                                    max(mailorder2$frequency)),rigth = T, labels = c(1,2,3,4,5))
mailorder2$M = cut(mailorder2$monetary, breaks = c(min(mailorder2$monetary)-1, 113, 181, 242, 299, 
                                                   max(mailorder2$monetary)),rigth = T, labels = c(1,2,3,4,5))
mailorder1$R = varhandle::unfactor(mailorder1$R)
mailorder1$F = varhandle::unfactor(mailorder1$F)
mailorder1$M = varhandle::unfactor(mailorder1$M)
mailorder2$R = varhandle::unfactor(mailorder2$R)
mailorder2$F = varhandle::unfactor(mailorder2$F)
mailorder2$M = varhandle::unfactor(mailorder2$M)

mean_pur = mailorder1 %>% select(R, F, M, purchase) %>% group_by(R, F, M) %>% 
  summarise(mean_purchase = mean(purchase))%>% arrange(desc(mean_purchase))

for( i in 1:nrow(mailorder2))
{
  for( j in 1:nrow(mean_pur))
  {
    if(mean_pur$R[j] == mailorder2$R[i] &
       mean_pur$F[j] == mailorder2$F[i] &
       mean_pur$M[j] == mailorder2$M[i])
    {
      mailorder2$mean_purchase[i] = mean_pur$mean_purchase[j]
    }
  }  
}


mailorder2 %>% select(purchase, mean_purchase) %>% arrange(desc(mean_purchase)) %>% 
  head(500) %>% summarise(mean = mean(purchase))
```

4. Apply the following linear regression model to the estimation sample. 
Purchase = 0 + 1(recency) + 2(frequency) + 3(monetary)
Based on the coefficient estimates from the regression, estimate the purchase probability of each of 2,000 customers in the validation sample. Select the top 500 customers and calculate the number of customers who actually made purchases.
```{r}
model = lm(purchase~recency+frequency+monetary, mailorder1)
pred = predict(model, mailorder2)

mailorder2$predict = pred

mailorder2 %>% select(purchase, recency, frequency, monetary, predict) %>% arrange(desc(predict)) %>% 
   head(500) %>% summarise(mean = mean(purchase))

```

Question 5. 
Propose a model of any form and do the same as above. (Your model will be evaluated in terms of the magnitude of improvement over the above models in validation sample.)

여기서부터 변수 다 넣고 실행
```{r}
# 회귀분석
model = lm(purchase~., mailorder1)
pred = predict(model, mailorder2)

mailorder2$predict = pred

mailorder2 %>% arrange(desc(predict)) %>% 
   head(500) %>% summarise(mean = mean(purchase))
```

```{r}
# 회귀분석(변수선택법 사용)
set.seed(1234)
mailorder1 = head(mailorder, 2000)
mailorder2 = tail(mailorder, 2000)

model = lm(purchase ~ gender + poly(monetary, 2) + poly(recency, 2) + poly(frequency, 2) + poly(duration, 2), mailorder1)
model = step(model, direction = 'both')
pred = predict(model, mailorder2)

mailorder2$predict = pred

mailorder2 %>% arrange(desc(predict)) %>% 
   head(500) %>% summarise(mean = mean(purchase))
```

```{r}
# 회귀분석 변수 장난치기
set.seed(1234)
mailorder1 = head(mailorder, 2000)
mailorder2 = tail(mailorder, 2000)

model = lm(purchase ~ gender + log(monetary) + poly(recency,2) + poly(frequency,2), mailorder1)
pred = predict(model, mailorder2)

mailorder2$predict = pred

mailorder2 %>% arrange(desc(predict)) %>% 
   head(500) %>% summarise(mean = mean(purchase))
```

```{r}
# glm으로 변수 장난치기
set.seed(1234)
mailorder1 = head(mailorder, 2000)
mailorder2 = tail(mailorder, 2000)

model = glm(purchase ~ gender + log(monetary) + poly(recency,2) + poly(frequency,2), mailorder1, family = 'binomial')
pred = predict(model, mailorder2, type = 'response')

mailorder2$predict = pred

mailorder2 %>% arrange(desc(predict)) %>% head(500) %>% summarise(mean = mean(purchase))
```

```{r}
# XG Boosting

```


```{r}
# 로지스틱 회귀분석
model = glm(purchase~., mailorder1, family = 'binomial')
pred = predict(model, mailorder2, type = 'response')

mailorder2$predict = pred

mailorder2 %>% arrange(desc(predict)) %>% head(500) %>% summarise(mean = mean(purchase))
```

```{r}
# ridge regresssion
library(glmnet)
set.seed(1234)
mailorder1 = head(mailorder, 2000)
mailorder2 = tail(mailorder, 2000)

train_x = model.matrix(purchase~., mailorder1)[,-c(1,2)]
train_y = mailorder1$purchase

test_x = model.matrix(purchase~., mailorder2)[,-c(1,2)]
test_y = mailorder2$purchase

set.seed(1234)
cv.out = cv.glmnet(train_x, train_y, alpha=0)
plot(cv.out)
cv.out$lambda.min


grid = 10^seq(10,-2,length=100)
model = glmnet(train_x, train_y, alpha = 0, lambda = grid)

pred = predict(model, newx = test_x, s = 0.0083)

test = cbind(data.frame(test_y), data.frame(pred))

test %>% arrange(desc(X1)) %>% head(500) %>% summarise(mean = mean(test_y))
```

```{r}
# rasso regresssion
set.seed(1234)
mailorder1 = head(mailorder, 2000)
mailorder2 = tail(mailorder, 2000)

train_x = model.matrix(purchase~., mailorder1)[,-c(1,2)]
train_y = mailorder1$purchase

test_x = model.matrix(purchase~., mailorder2)[,-c(1,2)]
test_y = mailorder2$purchase

grid = 10^seq(10,-2,length=100)
lasso.mod=glmnet(train_x, train_y, alpha=1, lambda=grid)
plot(lasso.mod)

set.seed(1234)
cv.out=cv.glmnet(train_x, train_y, alpha=1)
plot(cv.out)
cv.out$lambda.min


grid = 10^seq(10,-2,length=100)
model = glmnet(train_x, train_y, alpha = 1, lambda = grid)

pred = predict(model, newx = test_x, s = 6.409946e-05)

test = cbind(data.frame(test_y), data.frame(pred))

test %>% arrange(desc(X1)) %>% head(500) %>% summarise(mean = mean(test_y))
```

```{r}
# svm
set.seed(1234)
mailorder1 = head(mailorder, 2000)
mailorder2 = tail(mailorder, 2000)

model = e1071::svm(purchase ~ monetary + recency + frequency + duration, mailorder1)
pred = predict(model, mailorder2)

mailorder2$predict = pred
mailorder2 %>% arrange(desc(predict)) %>% head(500) %>% summarise(mean = mean(purchase))
```

```{r}
# naiveBayes
set.seed(1234)
mailorder1 = head(mailorder, 2000)
mailorder2 = tail(mailorder, 2000)

mailorder3 = mailorder1
mailorder4 = mailorder2

mailorder3$purchase = as.factor(mailorder3$purchase)
mailorder4$purchase = as.factor(mailorder4$purchase)

model = e1071::naiveBayes(purchase ~ monetary + recency + frequency + duration, mailorder3)
pred = predict(model, mailorder4)

mailorder4$predict = pred
mailorder4$purchase = as.numeric(mailorder4$purchase) - 1
mailorder4 %>% arrange(desc(predict)) %>% head(500) %>% summarise(mean = mean(purchase))
```

```{r}
# randomForest
set.seed(1234)
mailorder1 = head(mailorder, 2000)
mailorder2 = tail(mailorder, 2000)

mailorder3 = mailorder1
mailorder4 = mailorder2

mailorder3$purchase = as.factor(mailorder3$purchase)
mailorder4$purchase = as.factor(mailorder4$purchase)

model = randomForest::randomForest(purchase ~ gender + monetary + recency + frequency + duration, mailorder3)
pred = predict(model, mailorder4)

mailorder4$predict = pred
mailorder4$purchase = as.numeric(mailorder4$purchase) - 1
mailorder4 %>% arrange(desc(predict)) %>% head(500) %>% summarise(mean = mean(purchase))
```

```{r}
# 스케일링
set.seed(1234)
mailorder1 = head(mailorder, 2000)
mailorder2 = tail(mailorder, 2000)

scale_train = as.data.frame(scale(mailorder1[,-c(1,2,7)]))
scale = cbind(scale_train, mailorder1[,7])
colnames(scale)[5] = 'purchase'

scale_test = as.data.frame(scale(mailorder2[,-c(1,2,7)]))
scale2 = cbind(scale_test, mailorder2[,7])
colnames(scale2)[5] = 'purchase'

model = lm(purchase~., scale)
pred = predict(model, scale2)


scale2$predict = pred
scale2 %>% arrange(desc(predict)) %>% head(500) %>% summarise(mean = mean(purchase))
```

```{r}
# bootstrap
mailorder3 = mailorder1 %>% na.omit() %>% select(purchase, recency, frequency, monetary)
mailorder4 = mailorder2 %>% na.omit() %>% select(purchase, recency, frequency, monetary)

model_fit = lm(purchase ~ ., mailorder3)








```


















```{r}
# 회귀분석 ploy + 다른변수 추가
set.seed(1234)
mailorder1 = head(mailorder, 2000)
mailorder2 = tail(mailorder, 2000)

train_x = model.matrix(purchase~gender+poly(monetary,2)+poly(recency,2)+poly(frequency,2)+poly(duration,2), mailorder1)[,-1]
train_y = mailorder1$purchase

test_x = model.matrix(purchase~gender+poly(monetary,2)+poly(recency,2)+poly(frequency,2)+poly(duration,2), mailorder2)[,-1]
test_y = mailorder2$purchase

set.seed(1234)
cv.out = cv.glmnet(train_x, train_y, alpha=0)
plot(cv.out)
cv.out$lambda.min


grid = 10^seq(10,-2,length=100)
model = glmnet(train_x, train_y, alpha = 0, lambda = grid)

pred = predict(model, newx = test_x, s = cv.out$lambda.min)

test = cbind(data.frame(test_y), data.frame(pred))

test %>% arrange(desc(X1)) %>% head(500) %>% summarise(mean = mean(test_y))
```

```{r}
# 회귀분석 ploy
mailorder3 = mailorder1 %>% select(purchase, recency, frequency, monetary)
mailorder4 = mailorder2 %>% select(purchase, recency, frequency, monetary)

model = lm(purchase ~ poly(recency,2) + poly(frequency,2) + poly(monetary,2), mailorder3)

pred = predict(model, mailorder4)

mailorder4$predict = pred

mailorder4 %>% arrange(desc(predict)) %>% 
   head(500) %>% summarise(mean = mean(purchase))

```

```{r}
# 로지스틱 회귀분석
mailorder3 = mailorder1 %>% select(purchase, recency, frequency, monetary)
mailorder4 = mailorder2 %>% select(purchase, recency, frequency, monetary)

model = glm(purchase~., mailorder3, family = 'binomial')
pred = predict(model, mailorder4, type = 'response')

mailorder4$predict = pred

mailorder4 %>% arrange(desc(predict)) %>% head(500) %>% summarise(mean = mean(purchase))
```

```{r}
# 스케일링
mailorder3 = mailorder1 %>% select(purchase, recency, frequency, monetary)
mailorder4 = mailorder2 %>% select(purchase, recency, frequency, monetary)

scale_train = as.data.frame(scale(mailorder3[,-1]))
scale = cbind(scale_train, mailorder3[,1])
colnames(scale)[4] = 'purchase'

scale_test = as.data.frame(scale(mailorder4[,-1]))
scale2 = cbind(scale_test, mailorder4[,1])
colnames(scale2)[4] = 'purchase'

model = lm(purchase~recency+frequency+monetary, scale)
pred = predict(model, scale2)


scale2$predict = pred
scale2 %>% arrange(desc(predict)) %>% head(500) %>% summarise(mean = mean(purchase))
```

```{r}
# svm
mailorder3 = mailorder1 %>% select(purchase, recency, frequency, monetary)
mailorder4 = mailorder2 %>% select(purchase, recency, frequency, monetary)

model = e1071::svm(purchase~., mailorder3)
pred = predict(model, mailorder4)

mailorder4$predict = pred
mailorder4 %>% arrange(desc(predict)) %>% head(500) %>% summarise(mean = mean(purchase))
```

```{r}
# nnet 개망했고.
mailorder3 = data.matrix(mailorder1 %>% select(purchase, recency, frequency, monetary))

# Build nn model
# first layers
my_input = mx.symbol.Variable('data')
fc1 = mx.symbol.FullyConnected(data = my_input, num.hidden = 200, name = 'fc1')
relu1 = mx.symbol.Activation(data = fc1, act.type = 'relu', name = 'relu1')

# second layers
fc2 = mx.symbol.FullyConnected(data = relu1, num.hidden = 100, name = 'fc2')
relu2 = mx.symbol.Activation(data = fc2, act.type = 'relu', name = 'relu2')

# third layers
fc3 = mx.symbol.FullyConnected(data = relu2, num.hidden = 2, name = 'fc3')

# softmax
softmax = mx.symbol.SoftmaxOutput(data = fc3, name ='sm')

# training
device = mx.cpu()
model = mx.model.FeedForward.create(softmax, optimizer = 'sgd', array.batch.size = 10, num.round = 300,
                                    learning.rate = 0.1, X = mailorder3[,-1], y = mailorder3[,1], 
                                    ctx = device,
                                    eval.metric = mx.metric.accuracy, array.layout = 'rowmajor', 
                                    epoch.end.callback = mx.callback.log.train.metric(100))

# testing
mailorder4 = data.matrix(mailorder2 %>% select(purchase, recency, frequency, monetary))
pred = predict(model, mailorder4[,-1], array.layout = "rowmajor")
pred_labels = max.col(t(pred)) - 1
table(mailorder4[,1], pred_labels)
```

```{r}

```

















