---
title: "Homework"
author: "Hyeonho Lee"
date: "2018년 8월 17일"
output: 
  pdf_document: 
    latex_engine: xelatex
  html_document: default
  word_document:
    highlight: tango
mainfont: NanumGothic
---

(homework) Re-create the data graphic, “Youngest Male Names” (again, your result will be different from the chart below). You can recycle some of the codes above. 
In particular, the youngest men names are given by the ascending order or median_age. 
Your chart should be restricted to birth names given to at least 100,000 male Americans since 1900.
Use filter() to filter names with at least 100,000  est_num_alive. Can you make the color of the bars Carolina blue?


```{r}
# library(Hmisc)
# library(mdsr)
# library(babynames)
# library(dplyr)
```

```{r include = FALSE}
library(Hmisc)
library(mdsr)
library(babynames)
library(dplyr)
```

```{r}
BabynamesDist <- make_babynames_dist()
head(BabynamesDist, 2)
```

```{r}
com_fem <- BabynamesDist %>%
  filter(sex == "M") %>% filter(est_alive_today!=0) %>%
  group_by(name) %>%
  summarise(
    N = n(), est_num_alive = sum(est_alive_today),
    q1_age = wtd.quantile(age_today, est_alive_today, probs = 0.25),
    median_age = wtd.quantile(age_today, est_alive_today, probs = 0.5),
    q3_age = wtd.quantile(age_today, est_alive_today, probs = 0.75)) %>% 
  filter(est_num_alive >= 100000) %>%
  arrange(median_age) %>% 
  head(25)
```

```{r}
com_fem
```

```{r}
w_plot <- ggplot(
  data = com_fem, 
  aes(x = reorder(name, -median_age),  y = median_age)) + 
  xlab(NULL) + 
  ylab("Age (in years)") +
  ggtitle("Median ages for males with the 25 names")
```

```{r warning=FALSE}
w_plot + 
  geom_linerange(
    aes(ymin = q1_age, ymax = q3_age),
    color = "#6495ED", 
    size = 5, 
    alpha = 1) + 
  geom_hline(aes(yintercept = 5), linetype = 'dotted') +
  geom_hline(aes(yintercept = 10), linetype = 'dotted') +
  geom_hline(aes(yintercept = 15), linetype = 'dotted') +
  geom_hline(aes(yintercept = 20), linetype = 'dotted') +
  geom_hline(aes(yintercept = 25), linetype = 'dotted') +
  geom_hline(aes(yintercept = 30), linetype = 'dotted') +
  geom_point(fill = "#ed3324", colour = "white", size = 4, shape = 21) +
  geom_point(aes(y = 28.5, x = 21.9), fill = "#ed3324", colour = "white", size = 4, shape = 21) +
  #theme(panel.background = element_rect(fill='gray')) +
  geom_text(aes(y = 8.25, x = 14.2, label = '◀')) +
  geom_text(aes(y = 9.2, x = 14.2, label = '25th')) +
  geom_text(aes(y = 22.8, x = 14.2, label = '▶')) +
  geom_text(aes(y = 20.3, x = 14.2, label = '75th percentile')) +
  geom_text(aes(y = 30, x = 22, label = 'median')) +
  scale_y_continuous(position = "bottom", breaks = c(5, 10, 15, 20, 25, 30), 
                     labels = c("5 yrs old", "10", "15", "20", "25", "30")) +
  theme(plot.title = element_text(face = 'bold', size = 16),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        axis.ticks = element_blank(), plot.caption = element_text(size = 10)) +
  coord_flip()
```





